ShabbyPages: A Recipe for Repeatable, Synthetic, Modern Document Images

### 2023-02-04 paper/paper.tex
add patch matrix image
fix paper riding

\documentclass[runningheads]{llncs}
\usepackage{graphicx}
\usepackage[colorlinks]{hyperref}
\hypersetup{
    colorlinks = false,
    linkbordercolor = {blue}
}
\usepackage{listings}
\usepackage{courier}
\renewcommand{\floatpagefraction}{.8}
%
\begin{document}

@@

\author{Anonymous ICDAR 2023 submission}

@@

\begin{figure}
\centering
\includegraphics[width=0.98\columnwidth, frame]{Article_Hero_Picture_Shadow.png}
\caption{Example ShabbyPages image, before (left side) and after augmentationi (right side).} \label{fig1}
\end{figure}

@@

>>>>

\documentclass[runningheads]{llncs}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{pifont}
\usepackage[colorlinks]{hyperref}
\usepackage[dvipsnames]{xcolor}
\hypersetup{
    colorlinks = false,
    linkbordercolor = {blue}
}
\usepackage{listings}
\usepackage{courier}

% check mark and x for table
\newcommand{\cmark}{{\color{ForestGreen}\ding{51}}}%
\newcommand{\xmark}{{\color{Maroon}\ding{55}}}%

\def\rot{\rotatebox}

\renewcommand{\floatpagefraction}{.8}
%
\begin{document}

@@

\author{Anonymous ICDAR 2023 submission}
\titlerunning{ShabbyPages}

@@

\begin{figure}
\centering
\includegraphics[width=0.98\columnwidth, frame]{matrix.png}
\caption{Sample patches from ShabbyPages.} \label{fig1}
\end{figure}

@@

% WIP: this table is a work-in-progress
\begin{table}[]
    \centering
    \caption{Summary of datasets for document denoising and document binarization tasks.}
    \label{tab:datasets}
    \begin{tabular}{lcllllllll}
        \textbf{Dataset} &
        \rot{80}{\textbf{Dataset Size}}
            & \rot{80}{\textbf{Synthetic Noise}}
            & \rot{80}{\textbf{Ground-Truths}}
            & \rot{80}{\textbf{Diversity}}
            & \rot{80}{\textbf{Font size}}
            & \rot{80}{\textbf{Paper styles}}
            & \rot{80}{\textbf{Multilingual}}
            & \rot{80}{\textbf{Contains graphics}}
            & \rot{80}{\textbf{Pre-categorized}} \\
            \midrule
         ShabbyPages (ours) & 6,202 & \cmark & \cmark & 0.488 & Multi & Multi & \cmark & \cmark & \xmark \\
         NoisyOffice \cite{ref_NoisyOffice} & 72  & \cmark & \cmark & 0.317 & 16pt & 1 & \xmark & \xmark & \xmark \\
         DocCreator & & & & & & & & & \\
         DIBCO-9 \cite{dibco-09} & & & & & & & & & \\
         DIBCO-10 \cite{dibco-10} & & & & & & & & & \\
         DIBCO-11 \cite{dibco-11} & & \xmark & \cmark & & multi & Multi & \cmark & \xmark & \xmark \\
         DIBCO-12 \cite{dibco-12} & & \xmark & & & & & & & \\
         DIBCO-13 \cite{dibco-13} & & \xmark & & & & & & & \\
         H-DIBCO-14 \cite{dibco-14} & & \xmark & & & & & & & \\
         H-DIBCO-16 \cite{dibco-16} & & \xmark & & & & & & & \\
         DIBCO-17 \cite{dibco-17} & & \xmark & & & & & & & \\
         H-DIBCO-18 \cite{dibco-18} & & \xmark & & & & & & & \\
         DIBCO-19 \cite{dibco-19} & & \xmark & & & & & & & \\
         Bickley Diary \cite{bickley-diary} & & & & & & & & & \\
         LS-HDIB \cite{ls-hdib-2021} & & \cmark & & & & & & & \\
         \bottomrule
    \end{tabular}
\end{table}
